The Astropy Project

### 2017-11-24 main.tex
Rephrasing the motivation section for choosing Python

The development of the \astropypkg core package began as a largely
community-driven effort to standardize core functionality for astronomical
software in \python.
In this way, its genesis differs from but builds upon many substantial and
% * <bsipocz@gmail.com> 2017-11-13T13:13:08.884Z:
%
% how do astroy builds upon these? or it's more like builds upon the developer experience?
%
%
% ^.
former astronomical software development efforts that were commissioned or
initiated through large institutional support, for example IRAF \citep[developed
at NOAO;][]{IRAF}, MIDAS \citep[developed at ESO;][]{MIDAS}, or Starlink
\citep[originally developed by a consortium of UK institutions and now
maintained by the East Asian Observatory;][]{starlink1982,starlink2013}.
More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}.
\python\footnote{\url{https://www.python.org/}} is an increasingly popular,
general-purpose programming language that is available under a permissive open
source software license free of charge for all major operating systems.
Stable and well-developed packages provide support for array representation and arithmetic
\citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy};][]{numpy}, and publication-quality plotting
\citep[\package{matplotlib};][]{matplotlib}. Tens of thousands of other packages
are available which can help with tasks that are not astronomy specific but
might be performed in the course of astronomical research, for example interfacing with databases or statistical inference.

\python has become especially popular in the quantitative sciences,
where researchers must simultaneously produce research, perform data analysis,
and develop software.
A large part of this success owes itself to a vibrant community of developers
and a continuously-growing ecosystem of tools and web services that enable
easier collaboration on software development, easier writing and sharing of
software documentation, and continuous testing and validation of software.
More recently, package managers such as
Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation
process for most packages, therefore significantly reducing the barrier to entry
for using many such libraries.

@@

\subsection{Astropy development model}
% draft by Adrian PW and Erik T.
Code is contributed to the \astropypkg core package or modified through ``pull
requests'' (via \github) that often contain several \texttt{git} commits.
Pull requests may fix bugs, implement new features, or improve or modify the
infrastructure that supports the development and maintenance of the package.
Individual pull requests are generally limited to a single conceptual addition
or modification to make code review tractable.
Pull requests that modify or add code to a specific subpackage must be reviewed
and approved by one of the subpackage maintainers before it is merged into the
core codebase.
Bugs and feature requests are reported via the \github issue tracker and labeled
with a set of possible labels that help classify and organize the issues.
The development workflow is detailed in the \astropypkg
documentation.\footnote{\emph{How to make a code contribution},
\url{http://docs.astropy.org/en/stable/development/workflow/development_workflow.html}}

>>>>

The development of the \astropypkg core package began as a largely
community-driven effort to standardize core functionality for astronomical
software in \python.
In this way, its genesis differs from but builds upon many substantial and
% * <bsipocz@gmail.com> 2017-11-13T13:13:08.884Z:
%
% how do astroy builds upon these? or it's more like builds upon the developer experience?
%
%
% ^.
former astronomical software development efforts that were commissioned or
initiated through large institutional support, for example IRAF \citep[developed
at NOAO;][]{IRAF}, MIDAS \citep[developed at ESO;][]{MIDAS}, or Starlink
\citep[originally developed by a consortium of UK institutions and now
maintained by the East Asian Observatory;][]{starlink1982,starlink2013}.
More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}.

\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
programming language that is available under a permissive open source software license free of
charge for all major operating systems. The programming language has become especially popular
in the quantitative sciences, where researchers must simultaneously produce research, perform 
data analysis and develop software. A large part of this success owes itself to the vibrant 
community of developers and a continuously-growing ecosystem of tools, web services and stable
well-developed packages that enable easier collaboration on software development, easier 
writing and sharing of software documentation and continuous testing and validation of 
software. While the programming language provides support for array representation \& 
arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific 
computing \citep[\package{scipy};][]{numpy}, publication-quality plotting 
\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high quality and easy 
to use packages are available which can help with tasks that are not astronomy specific but 
might be performed in the course of astronomical research, for example, interfacing with 
databases or statistical inferences. More recently, the development of package managers such as
Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation process for
most packages significantly reducing the barrier to entry for using many such libraries.

@@

\subsection{Astropy development model}
% draft by Adrian PW and Erik T.
Code is contributed to the \astropypkg core package or modified through ``pull
requests'' (via \github) that often contain several \texttt{git} commits.
Pull requests may fix bugs, implement new features, or improve or modify the
infrastructure that supports the development and maintenance of the package.
Individual pull requests are generally limited to a single conceptual addition
or modification to make code review tractable.
Pull requests that modify or add code to a specific subpackage must be reviewed
and approved by one of the subpackage maintainers before it is merged into the
core codebase.
Bugs and feature requests are reported via the \github issue tracker and labeled
with a set of possible labels that help classify and organize the issues.
The development workflow is detailed in the \astropypkg
documentation.\footnote{\emph{How to make a code contribution}, \url{http://docs.
astropy.org/en/stable/development/workflow/development_workflow.html}}
